Does freshwater connectivity influence phosphorus retention in lakes?

### 2019-01-23 manuscript/manuscript.Rmd
fight with docker permissions

Prior studies at regional extents have shown that P retention in streams and rivers is largely determined by the fate of the particulate load fraction \citep{cushingTransportDynamicsFine1993, kronvang1992, russell1998, vanni2001}. For instance, the findings of \citet{jarvie2011} show that riverine P loads can be controlled by nonpoint-source P delivery of particulate P. Therefore, it stands to reason that P retention in lakes may also be largely determined by the fate of the particulate load fraction. However, in the context of our broad-scale study it is difficult to examine this relationship because although we have estimates of nonpoint versus point source loading we do not have explicit estimates of particulate load fraction for large numbers of lakes. Unfortunately, we cannot use nonpoint source loading as a direct proxy for particulate load fraction because the two quantities do not have a consistent relationship. For example, \citet{russell1998} report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90% while \citet{djodjicSingleFieldsRiver2018} report that this fraction can be anywhere between 33 and 80%. This may explain why prior broad scale studies that estimate lake P retention have not attempted to estimate separate effects of particulate versus dissolved loading \citep{alexander2008, brett2008}.

>>>>

Prior studies at regional extents have shown that P retention in streams and rivers is largely determined by the fate of the particulate load fraction \citep{cushingTransportDynamicsFine1993, kronvang1992, russell1998, vanni2001}. For instance, the findings of \citet{jarvie2011} show that riverine P loads can be controlled by nonpoint-source P delivery of particulate P. Therefore, it stands to reason that P retention in lakes may also be largely determined by the fate of the particulate load fraction. However, in the context of our broad-scale study it is difficult to examine this relationship because although we have estimates of nonpoint versus point source loading we do not have explicit estimates of particulate load fraction for large numbers of lakes. Unfortunately, we cannot use nonpoint source loading as a direct proxy for particulate load fraction because the two quantities do not have a consistent relationship. For example, \citet{russell1998} report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90\% while \citet{djodjicSingleFieldsRiver2018} report that this fraction can be anywhere between 33 and 80\%. This may explain why prior broad scale studies that estimate lake P retention have not attempted to estimate separate effects of particulate versus dissolved loading \citep{alexander2008, brett2008}.
